The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-06-27 WavesData-2019/LatexNotes/notes.tex
NM

\subsection{The Korteweg–de Vries equation with variable depth}
Consider waves propagating unidirectionally in shallow water. Consider the surface displacement $\eta(x,t)$ and the reference frame moving with the local wave speed $\xi = x - ct$, where $c = \sqrt{g \depth}$ is the wave speed, $g$ gravity, and $\depth$ the local depth.
To first-correction in small amplitude, surface displacements are governed by the Korteweg–de Vries equation (KdV), which in dimensional form is given by
\begin{equation}
2 \eta_t + \frac{3 c}{\depth} \eta \eta_{\xi} + \frac{c \depth^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}

@@

We introduce the following characteristic scales
\begin{align}
&a = \mean{\eta^2}^{1/2} 
&&\mbox{\em upstream characteristic wave amplitude} \\
&\lamup = \sqrt{g \dup} / \freqp
&&\mbox{\em upstream characteristic wave length}
\end{align}
and the dimensionless variables
\begin{align}
&u = \eta/a
&&\mbox{\em dimensionless displacement} \\
&\tilde{x} = \xi/\lamup = (x-ct)/\lamup
&&\mbox{\em dimensionless position} \\
& \tilde{t} = 
\end{align}

>>>>

\subsection{The Korteweg–de Vries equation with variable depth}
Consider waves propagating unidirectionally in shallow water. Consider the surface displacement $\eta(x,t)$ and the reference frame moving with the local wave speed $\xi = x - ct$, where $c = \sqrt{g \depth}$ is the wave speed, $g$ gravity, and $\depth$ the local depth.
To first-correction in small amplitude, surface displacements are governed by the Korteweg–de Vries equation (KdV), which in dimensional form is given by
\begin{equation}
2 \eta_t + \frac{3 c}{\depth} \eta \eta_{\xi} + \frac{c \depth^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
% The coefficients and scales can be verified on Wolfram KdV page (but what about the sign?). I would like an official source as confirmation though.

@@

We introduce the following characteristic scales
\begin{align}
&a = \mean{\eta^2}^{1/2} 
&&\mbox{\em upstream characteristic wave amplitude} \\
&\lamup = \sqrt{g \dup} / \freqp
&&\mbox{\em upstream characteristic wave length}
\end{align}
and the dimensionless variables
\begin{align}
&u = \eta/a
&&\mbox{\em dimensionless displacement} \\
&\tilde{x} = \frac{2 \pi \xi}{\lamfac \lamup} = \frac{2 \pi (x-ct)}{\lamfac \lamup}
&&\mbox{\em dimensionless position} \\
& \tilde{t} = 
\end{align}
